Inference failure: Confound and control in BBS experiments

### 2016-05-09 simulation/statfail.Rmd
crossref, request to run locally

A Shiny app that allows you to more closely individual simulated experiments for a given set of simulation parameters is available in the GitHub repository. This will be posted on [shinyapps.io](https://www.shinyapps.io/) as soon as we RStudio updates their server version of R or we have a chance to install and test an extra, older version of R.

>>>>

A Shiny app that allows you to more closely individual simulated experiments for a given set of simulation parameters is available in the GitHub repository and on [shinyapps.io](https://palday.shinyapps.io/statfail/).
If you're going to do lots of computations, please run the app locally so that server time remains available for others.
